Regularization Techniques for PSF--Matching Kernels. II. Pre--Filtering of Input Images

### 2015-02-24 submit/ms.tex
Acknowledgement cribbed from Chang et al

\section*{Acknowledgments}
LSST blurb here.

>>>>

\section*{Acknowledgments}
LSST project activities are supported in part by the National Science Foundation through Governing Cooperative Agreement 0809409 managed by the Association of Universities for Research in Astronomy (AURA), and the Department of Energy under contract DE-AC02-76-SFO0515 with the SLAC National Accelerator Laboratory. 
Additional LSST funding comes from private donations, grants to universities, and in--kind support from LSSTC Institutional Members.
